%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[11pt]{article}
\usepackage{fontspec}

% ---- CONDITIONALS
\usepackage{ifthen}
\usepackage{ifxetex}
\usepackage{xifthen}
\newcommand*{\ifempty}[3]{\ifthenelse{\isempty{#1}}{#2}{#3}}

% ---- DOCUMENT LAYOUT
\usepackage{geometry}
\geometry{a4paper,textwidth=5.3in,textheight=8.7in,marginparsep=7pt,marginparwidth=.8in}
\setlength\parindent{0in}

% ---- COLORS
\usepackage[usenames,dvipsnames]{color}
\definecolor{Black}{rgb}{0,0,0}
\definecolor{Gray}{rgb}{0.45,0.45,0.45}
\definecolor{Blue}{rgb}{0.0,0.0,1.0}

% ---- FONTS
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text}

\newcommand*{\fontdir}[1][fonts/]{\def\@fontdir{#1}}
\fontdir
\newfontfamily\sansfont[
    Path=\@fontdir,
    UprightFont=*-Regular,
    ItalicFont=*-It,
    BoldFont=*-Bold,
    BoldItalicFont=*-BoldIt,
]{SourceSansPro}

\setmainfont[
    Path=\@fontdir,
    UprightFont=*12-Regular,
    ItalicFont=*12-Italic,
]{EBGaramond}

\usepackage{fontawesome}

\newcommand{\amper}{~\&~}

% ---- FONT STYLES
\newcommand*{\headerstyle}       [1]{{\Huge       \color{Black} \bfseries \scshape \sansfont{#1}}}
\newcommand*{\headercontactstyle}[1]{{\normalsize \color{Gray}  \bfseries \scshape \sansfont{#1}}}
\newcommand*{\headerurlstyle}    [1]{{\normalsize \color{Gray}                     \sansfont{#1}}}
\newcommand*{\sectionstyle}      [1]{{\normalsize \color{Black} \bfseries \scshape \sansfont{#1}}}
\newcommand*{\footerstyle}       [1]{{\scriptsize \color{Gray}            \scshape \sansfont{#1}}}
\newcommand*{\marginstyle}       [1]{{\small      \color{Gray}  #1}}

% ---- HEADER/FOOTER
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagenumbering{arabic}
\pagestyle{fancy}
\renewcommand\headrulewidth{0pt}
\renewcommand\footrulewidth{0pt}
\fancyhf{}
\fancyfoot[L]{\footerstyle{last updated: \today}}
\fancyfoot[C]{\footerstyle{typeset in \XeTeX}}
\fancyfoot[R]{\footerstyle{page~\thepage~of~\pageref{LastPage}}}

% ---- MARGIN
\usepackage{marginnote}
\newcommand{\notes}[1]{\marginnote{\marginstyle{#1}}}
\newcommand{\cvsection}[1]{\vspace{0.2cm}\hrule\vspace{0.15cm}\sectionstyle{#1}}
\renewcommand*{\raggedrightmarginnote}{}
\reversemarginpar

% ----- PDF SETUP
\usepackage[bookmarks, colorlinks, breaklinks,
	pdftitle={Gaurav Chaurasia CV},
	pdfauthor={Gaurav Chaurasia},
	pdfproducer={http://nitens.org/taraborelli/cvtex}
]{hyperref}
\hypersetup{filecolor=Gray,urlcolor=Gray,linkcolor=Gray,citecolor=Gray}

% ----- PUBLICATIONS
\newcommand{\organization}[1]{{\large\scshape #1}}
\newcommand{\location}[1]{{\large\itshape #1}}
\newcommand{\jobtitle}[1]{{\itshape #1}}
\newcommand{\advisor}[1]{{\itshape (Advisor: #1)}}
\newcommand{\jobdesc}[1]{{#1}}
\newcommand{\thesis}[1]{{\scshape Dissertation}: #1}

\newcommand{\paper}[1]{{#1}}
\newcommand{\authors}[1]{{#1}}
\newcommand{\journal}[1]{{\itshape #1}}
\newcommand{\html}[1]{\href{#1}{{\scriptsize\scshape [www]}}}
\newcommand{\doi} [1]{\href{#1}{{\scriptsize\scshape [doi]}}}

\newcommand{\jreview}[3]{#2\dotfill#1} % {\href{#3}{#2}\dotfill#1}
\newcommand{\creview}[2]{#2\dotfill#1}

\newcommand{\position}[6]{
    \notes{#1}
    \organization{#3}\hfill\location{#4} \\
    \jobtitle{#2}\ifempty{#5}{}{~\advisor{#5}}
    \ifempty{#6}{}{\\ \jobdesc{#6}}
}

\newcommand{\publication}[6]{
    \ifempty{#1}{}{\notes{#1}}
    \ifempty{#2}{}{\authors{#2}}.
    \ifempty{#3}{}{\paper{#3}},
    \ifempty{#4}{}{\journal{#4}}.~
    \ifempty{#5}{}{\html{#5}}
    \ifempty{#6}{}{\doi{#6}}
}

\usepackage{enumitem}
\newenvironment{cvitems}{
    \setlength{\leftmargini}{0cm}
    \setlength{\itemindent}{0cm}
    \setlength{\labelsep}{0cm}
    \setlength{\topsep}{0cm}
    \begin{description}
}
{\end{description}}
\newenvironment{shortcvitems}{
    \begin{cvitems}
    [noitemsep]
}
{\end{cvitems}}

\newcommand{\mailicon}{{\faEnvelope~~}}
\newcommand{\homeicon}{{\faHome~~}}
\newcommand{\www} [1]{{\href       {#1}{\color{Gray} \homeicon #1}}}
\newcommand{\mail}[1]{{\href{mailto:#1}{\color{Gray} \mailicon #1}}}

% ----- DOCUMENT
\begin{document}
\begin{center}
\headerstyle{gaurav chaurasia} \\
\headercontactstyle{disney research zurich, stampfenbachstrasse 48, zurich, switzerland} \\
\headerurlstyle{
    \mail{gchauras@mit.edu} \quad \www{http://people.csail.mit.edu/gchauras/}} \\
\vspace{0.3cm}
\end{center}

% -----------------------------------------------------------------------------
%
\cvsection{research interests}
\begin{shortcvitems}
\item Image-based rendering, 3D reconstruction
\item Computational photography using neural networks
\item GPU accelerated image processing
\end{shortcvitems}

% -----------------------------------------------------------------------------

\cvsection{experience}
\begin{cvitems}
\item \position
{2015-}
{Postdoctoral Associate (Computer vision group)}
{Disney Research Zurich}
{Zurich, Switzerland}
{}
{}

\item \position
{2014-2015}
{Postdoctoral Associate}
{Massachusetts Institute of Technology}
{Cambridge MA, USA}
{Prof. Fr{\'e}do Durand}
{}
\end{cvitems}

% -----------------------------------------------------------------------------

\cvsection{education}
\begin{cvitems}
\item \position
{2010-2014}
{Ph.D in Computer Science}
{Inria}
{Sophia Antipolis, France}
{Dr. George Drettakis}
{\thesis{Algorithms \amper perceptual analysis for interactive free viewpoint image-based navigation}}

\item \position
{2009-2010}
{M.Sc in Computer Science}
{ENSIMAG}
{Grenoble, France}
{}
{}

\item \position
{2005-2009}
{B.Tech in Computer Science}
{Indian Institute of Technology Delhi}
{New Delhi, India}
{Prof. Subodh Kumar}
{\thesis{Real time traffic simulation}}
\end{cvitems}

% -----------------------------------------------------------------------------

\cvsection{visiting positions}
\begin{cvitems}
\item \position
{Aug 2013}
{Visiting student}
{Massachusetts Institute of Technology}
{Cambridge MA, USA}
{Prof. Fr{\'e}do Durand}
{Parallel execution of non-parallel recursive filters.}

\item \position
{Aug 2012}
{Visiting student}
{University of California Berkeley}
{Berkeley CA, USA}
{Prof. Ravi Ramamoorthi}
{Procedural noise functions for synthesizing non-Gaussian textures.}

\item \position
{Feb-Jun 2010}
{Research intern}
{Inria}
{Sophia Antipolis, France}
{Dr. George Drettakis}
{Image-based rendering for urban scenes.}

\item \position
{Summer 2008}
{Intern (Embedded graphics group)}
{Nvidia}{Bangalore, India}
{}
{OpenGL-ES extensions for GPU driver for embedded systems, OpenGL-ES 2.0 conformance test suite bugs.}

\item \position
{Summer 2007}
{Research intern}
{Dublin City University}
{Dublin, Ireland}
{Dr. Derek Molloy}
{Memory exercises as 3D games and user studies to test effect of 3D user interfaces on human recall.}
\end{cvitems}

% -----------------------------------------------------------------------------

\cvsection{publications}
\begin{cvitems}

\item \publication
{2016}
{M. Gharbi, \underline{G. Chaurasia}, S. Paris, F. Durand}
{Deep joint demosaicking and denoising}
{ACM Trans. Graph. (conditionally accepted SIGGRAPH Asia)}
{https://groups.csail.mit.edu/graphics/demosaicnet/}
{}

\item \publication
{2016}
{ST Digumarti, \underline{G. Chaurasia}, A. Taneja, A. Thomas, R. Siegwart, P. Beardsley}
{Underwater 3D capture using a low-cost commercial depth camera}
{IEEE Winter Conference on Applications of Computer Vision (WACV)}
{https://www.disneyresearch.com/publication/underwater-3d-capture/}
{http://dx.doi.org/10.1109/WACV.2016.7477644}

\item \publication
{2015}
{M. Gharbi, Y. Shih, \underline{G. Chaurasia}, J. Ragan-Kelley, S. Paris, F. Durand}
{Transform recipes for efficient cloud photo enhancement}
{ACM Trans. Graph. 34(6) (SIGGRAPH Asia)}
{https://groups.csail.mit.edu/graphics/xform_recipes/}
{http://dx.doi.org/10.1145/2816795.2818127}

\item \publication
{2015}
{S. Duch\^{e}ne, C. Riant, \underline{G. Chaurasia}, J. Lopez-Moreno, PY Laffont, S. Popov, A. Bousseau, G. Drettakis}
{Multi view intrinsic decomposition \amper relighting}
{ACM Trans. Graph. 34(5)}
{http://www-sop.inria.fr/reves/Basilic/2015/DRCLLPD15/}
{http://dx.doi.org/10.1145/2790060.2790063}

\item \publication
{2015}
{\underline{G. Chaurasia}, J. Ragan-Kelley, S. Paris, G. Drettakis, F. Durand}
{Compiling high performance recursive filters}
{High Performance Graphics}
{https://mit-gfx.github.io/recfilter/}
{http://dx.doi.org/10.1145/2790060.2790063}

\item \publication
{2015}
{M. Benoit, R. Guerchouche, PD Petit, E. Chapoulie, V. Manera, \underline{G. Chaurasia}, G. Drettakis, P. Robert}
{Is it possible to use highly realistic virtual reality in the elderly? A feasibility study with image-based rendering}
{Journal of Neuropsychiatric Disease and Treatment}
{http://www.dovepress.com/articles.php?article_id=20707}
{http://dx.doi.org/10.2147/NDT.S73179}

\item \publication
{2014}
{E. Chapoulie, R. Guerchouche, PD Petit, \underline{G. Chaurasia}, P. Robert, G. Drettakis}
{Reminiscence therapy using image-based rendering in VR}
{IEEE Virtual Reality}
{http://www-sop.inria.fr/reves/Basilic/2014/CGPCRD14/}
{http://dx.doi.org/10.1109/VR.2014.6802049}

\item \publication
{2013}
{\underline{G. Chaurasia}, S. Duchene, O. Sorkine-Hornung, G. Drettakis}
{Depth synthesis and local warps for plausible image-based navigation}
{ACM Trans. Graph. 32(3)}
{http://www-sop.inria.fr/reves/Basilic/2013/CDSD13/}
{http://dx.doi.org/10.1145/2487228.2487238}

\item \publication
{2013}
{P. Vangorp, C. Richardt, E.A. Cooper, \underline{G. Chaurasia}, M.S. Banks, G. Drettakis}
{Perception of perspective distortions in image-based rendering}
{ACM Trans. Graph. 32(4) (SIGGRAPH)}
{http://www-sop.inria.fr/reves/Basilic/2013/VRCCBD13/}
{http://dx.doi.org/10.1145/2461912.2461971}

\item \publication
{2011}
{\underline{G. Chaurasia}, O. Sorkine, G. Drettakis}
{Silhouette-aware warping for image-based rendering}
{Comput. Graph. Forum 30(4) (EGSR)}
{http://www-sop.inria.fr/reves/Basilic/2011/CSD11/}
{http://dx.doi.org/10.1111/j.1467-8659.2011.01981.x}

\item \publication
{2011}
{P. Vangorp, \underline{G. Chaurasia}, PY Laffont, R. Fleming, G. Drettakis}
{Perception of visual artifacts in image-based rendering of fa{\c c}ades}
{Comput. Graph. Forum 30(4) (EGSR)}
{http://www-sop.inria.fr/reves/Basilic/2011/VCLFD11/}
{http://dx.doi.org/10.1111/j.1467-8659.2011.01983.x}

\item \publication
{2011}
{M. Cabral, P. Vangorp, \underline{G. Chaurasia}, E. Chapoulie, M. Hachet, G. Drettakis}
{A multimode immersive conceptual design system for architectural modeling \amper lighting}
{IEEE Symposium on 3D User Interfaces (IEEE 3DUI)}
{http://www-sop.inria.fr/reves/Basilic/2011/CVCCHD11/}
{http://dx.doi.org/10.1109/3DUI.2011.5759211}

\item \publication
{2010}
{\underline{G. Chaurasia}, B.R. Selvamani, N. Gupta, S. Kumar}
{Virtual chaotic traffic simulation}
{Indian Conference on Computer Vision, Graphics \amper Image Processing (ICVGIP)}
{http://people.csail.mit.edu/gchauras/research/pubs/traffsim/}
{http://dx.doi.org/10.1145/1924559.1924604}

\end{cvitems}

% -----------------------------------------------------------------------------

\cvsection{professional activities}
\begin{cvitems}
\item \notes{Journal reviews}
    \jreview{2016}{ACM Transactions on Graphics}{http://tog.acm.org/} \\
    \jreview{2014}{ACM Transactions on Applied Perception}{http://tap.acm.org} \\
    \jreview{2015}{Computer Graphics Forum}{http://onlinelibrary.wiley.com/journal/10.1111/\%28ISSN\%291467-8659} \\
    \jreview{2015, 2016}{IEEE Transactions on Visualization and Computer Graphics}{http://www.computer.org/web/tvcg} \\
    \jreview{2016}{The Visual Computer}{http://link.springer.com/journal/371} \\
    \jreview{2015}{Computers \amper Graphics}{http://www.journals.elsevier.com/computers-and-graphics/} \\
    \jreview{2015}{IEEE Signal Processing Letters}{http://www.signalprocessingsociety.org/publications/periodicals/letters/} \\
    \jreview{2013}{Journal of Signal Image \amper Video Processing}{http://www.springer.com/engineering/signals/journal/11760}
\item \notes{Conference reviews}
    \creview{2012, 2016}{SIGGRAPH} \\
    \creview{2013}{SIGGRAPH Asia} \\
    \creview{2012, 2016}{Eurographics} \\
    \creview{2016}{High Performance Graphics} \\
    \creview{2014, 2015, 2016}{Pacific Graphics} \\
    \creview{2016}{Virtual Reality Science \& Technology}
\end{cvitems}

% -----------------------------------------------------------------------------

\cvsection{supervision \amper teaching}
\begin{shortcvitems}
\item \notes{Spring 2016}TA: Advanced Methods in Computer Graphics Seminar \href{https://graphics.ethz.ch/teaching/seminarSS16/home.php}{252-5704-00L} \dotfill ETH Zurich
\item \notes{Spring 2015}TA: Digital \& Computational Photography \href{https://stellar.mit.edu/S/course/6/sp15/6.815/index.html}{6.815/6.865} \dotfill MIT
\item \notes{Spring 2013}Co-supervised Kritarth Anand (undergraduate thesis) \dotfill INRIA Sophia Antipolis/IIT Delhi
\item \notes{Spring 2013}Co-supervised Arunim Samat (undergraduate thesis) \dotfill INRIA Sophia Antipolis/IIT Delhi
\end{shortcvitems}

% -----------------------------------------------------------------------------

\cvsection{scholarships \amper awards}
\begin{shortcvitems}
\item \notes{Aug 2010}PhD fellowship (\textit{Allocation de Recherche}) by the French ministry for PhD studies.
\item \notes{Aug 2009}Scholarship of Excellence (\textit{Bourse d'Excellence}) by ENSIMAG for Master's studies.
\item \notes{May 2007}Scholarship for 12 week research internship `ODCSSS-07' in Dublin by Science Foundation of Ireland.
\item \notes{Jun 2005}All India Rank 54 in IIT-JEE 2005 (entrance examination for Indian Institutes of Technology) amongst nearly 300,000 aspirants.
\end{shortcvitems}

% -----------------------------------------------------------------------------

% \cvsection{major curriculum projects}
% \notes{Jan 2010}3D Air Hockey with stereo vision and hand tracking (\textit{Course: Virtual Reality}) \\
% \notes{Apr 2009}Light Field Rendering using CUDA on GPU (\textit{Course: Parallel Programming}) \\
% \notes{Nov 2008}Ocean Simulation with Fast Fourier Transform on GPU (\textit{Course: Advanced Graphics}) \\
% \notes{Apr 2008}Content-based Search in Audio Files \\
% \notes{Apr 2008}Modeling Tool for Rendering Fractal Terrains (\textit{Course: Computer Graphics}) \\
% \notes{Apr 2008}Multi-threaded Secure Network File System with Encryption (\textit{Course: Operating Systems}) \\
% \notes{Jan 2008}Software Rasterizer for Viewing 3D Models (\textit{Course: Computer Graphics}) \\
% \notes{Apr 2007}Star Topology of Ports using VHDL on XILINX FPGA (\textit{Course: Digital Hardware Design})

% -----------------------------------------------------------------------------

\cvsection{technical skills}
\begin{cvitems}
\item C++, {\scshape Matlab}, OpenGL, GLSL, CUDA, OpenCV, Java, \LaTeX, SVN, Git, Bash, Vim, Visual Studio
\end{cvitems}

% -----------------------------------------------------------------------------

\cvsection{references}
\begin{cvitems}
\ifthenelse{\equal{1}{0}}
{%
\item Available on request.
}{%
\item Dr. George Drettakis \\ {\itshape Director of Research, INRIA Sophia Antipolis, France} \\
\www{http://www-sop.inria.fr/members/George.Drettakis/} \quad
\mail{george.drettakis@inria.fr}
%
\item Prof. Fr{\'e}do Durand \\ {\itshape Professor, Massachusetts Institute of Technology, Cambridge MA, USA} \\
\www{http://people.csail.mit.edu/fredo/} \quad
\mail{fredo@mit.edu}
%
\item Dr. Sylvain Paris \\ {\itshape Senior Researcher, Adobe Research, Cambridge MA, USA} \\
\www{http://people.csail.mit.edu/sparis/} \quad
\mail{sparis@adobe.com}
}
\end{cvitems}

\end{document}
